Generalized Plackett-Luce Likelihoods

### 2023-03-05 inst/jss_hyper3.Rnw
force it to include the figures explicitly

\begin{figure}[htbp]
  \begin{center}
<<figaba>>=
a <- seq(from = 0, by = 0.005, to = 1)
S <- function(a){log(a * (1 - a) / ((1 + a) * (3 - 2 * sqrt(2))))}
plot(a, S(a), type = 'b')
abline(h = c(0, -2))
abline(v = c(0.02438102, 0.9524271), col = 'red')
abline(v = sqrt(2) - 1)
@
\caption{A\label{ABA_likelihood} support function for $p_a$ with observation $a\succ b\succ a$.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
<<figabbabb,echo=FALSE>>=
f_aab <- function(a){a^2 / (1 + a)}
f_aba <- function(a){a * (1 - a) / (1 + a)^2}
f_baa <- function(a){(1 - a) / (1 + a)}

@@

\begin{figure}[htbp]
  \begin{center}
<<plotwilcoxlike,echo=FALSE>>=
a <- seq(from = 0.02, to = 0.8, len = 40)
L <- sapply(a, function(p){loglik(p, Hxy)})
plot(a, L - max(L), type = 'b')
abline(h = c(0, -2))
abline(v = c(0.24))
abline(v=c(0.5), lty=2)
@
\caption{A\label{wilcox_likelihood} support function for the Bradley-Terry
strength $p_a$ of permeability at term.  The evaluate of 0.24 is
shown; and the two-units-of support credible interval, which does not
exclude $H_0\colon p_a=0.5$ (dotted line), is also shown.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
<<testthejav, cache=TRUE>>=
(mj <- maxp(javelin))
dotchart(mj, pch = 16)
@
\caption{Maximum likelihood estimate for javelin throwers' Bradley-Terry strengths.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<plottheloglikcont,echo=FALSE>>=
colnames(M) <-  as.character(Ves)
plot(t(M), type = "b")
abline(h = c(0, -2))
abline(v = 0, lty = 2)
abline(v = log(0.32062833 / 0.11402735)) # these from mp
@
\caption{Profile \label{profliklogcont} likelihood for log-contrast
$\log\left(p_{\mbox{\tiny Vad}}/ p_{\mbox{\tiny Ves}}\right)$.  Null
of $p_{\mbox{\tiny Vad}}=p_{\mbox{\tiny Ves}}$ indicated with a dotted
line, and two-units-of-support limit indicated with horizontal lines;
thus the null is not rejected.}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
<<figaba, fig=TRUE>>=
a <- seq(from = 0, by = 0.005, to = 1)
S <- function(a){log(a * (1 - a) / ((1 + a) * (3 - 2 * sqrt(2))))}
plot(a, S(a), type = 'b')
abline(h = c(0, -2))
abline(v = c(0.02438102, 0.9524271), col = 'red')
abline(v = sqrt(2) - 1)
@
\caption{A\label{ABA_likelihood} support function for $p_a$ with observation $a\succ b\succ a$.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
<<figabbabb,echo=FALSE,fig=TRUE>>=
f_aab <- function(a){a^2 / (1 + a)}
f_aba <- function(a){a * (1 - a) / (1 + a)^2}
f_baa <- function(a){(1 - a) / (1 + a)}

@@

\begin{figure}[htbp]
  \begin{center}
<<plotwilcoxlike,echo=FALSE,fig=TRUE>>=
a <- seq(from = 0.02, to = 0.8, len = 40)
L <- sapply(a, function(p){loglik(p, Hxy)})
plot(a, L - max(L), type = 'b')
abline(h = c(0, -2))
abline(v = c(0.24))
abline(v=c(0.5), lty=2)
@
\caption{A\label{wilcox_likelihood} support function for the Bradley-Terry
strength $p_a$ of permeability at term.  The evaluate of 0.24 is
shown; and the two-units-of support credible interval, which does not
exclude $H_0\colon p_a=0.5$ (dotted line), is also shown.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
<<testthejav, cache=TRUE, fig=TRUE>>=
(mj <- maxp(javelin))
dotchart(mj, pch = 16)
@
\caption{Maximum likelihood estimate for javelin throwers' Bradley-Terry strengths.}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
<<plottheloglikcont,echo=FALSE,fig=TRUE>>=
colnames(M) <-  as.character(Ves)
plot(t(M), type = "b")
abline(h = c(0, -2))
abline(v = 0, lty = 2)
abline(v = log(0.32062833 / 0.11402735)) # these from mp
@
\caption{Profile \label{profliklogcont} likelihood for log-contrast
$\log\left(p_{\mbox{\tiny Vad}}/ p_{\mbox{\tiny Ves}}\right)$.  Null
of $p_{\mbox{\tiny Vad}}=p_{\mbox{\tiny Ves}}$ indicated with a dotted
line, and two-units-of-support limit indicated with horizontal lines;
thus the null is not rejected.}
\end{center}
\end{figure}
